Making Sequential Programs Deterministic

### 2019-04-06 java-design.tex
Remove confusing text

\subsection{Dataflow analysis and type refinement}\label{sec:dataflow-java}

@@

\todo{Mike doesn't understand the below.  An example would help clarify it.}

In the example above, even though the local variable \codeid{y} was declared to be \codeid{NonDet}, it gets
type refined to \codeid{Det} after the first assignment statement. As the result, the assignment of \codeid{y}
to a \codeid{Det} variable \codeid{z} is sound. In the following example,
\begin{verbatim}
void foo(@NonDet Object x, @Det Object y) {
    x = y;                // No type refinement for x.
    @Det Object z = x;    // Error.
}
\end{verbatim}
\theDeterminismChecker reports a warning at the second assignment statement of \codeid{foo}. Type refinement only applies to locals. Refining non-locals can result in side effects making the analysis unsound.

>>>>

\subsection{Type refinement via dataflow analysis}\label{sec:dataflow-java}

@@
